An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-27 draft.tex
nits: minor typos
Signed-off-by: Carson Farmer <carson.farmer@gmail.com>

Therefore, solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic resolution strategy can be insufficient in cases with complicated data structures or complicated network topologies. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may exceedingly costly (networking, storage, and computation) to regain consistency.

>>>>

Solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic resolution strategy can be insufficient in cases with complicated data structures or complicated network topologies. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may be exceedingly costly (networking, storage, and computation) to regain consistency.
